A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-10-15 ennv.tex
update

    % Title
    \node[align=center] at ($(current page.center)+(0,-5)$) 
    {
    {\fontsize{38}{1} \selectfont {{Neural Network Verification}}}\\[0.5in]

>>>>

    % Title
    \node[align=center] at ($(current page.center)+(0,-5)$) 
    {
        {\fontsize{24}{24} \selectfont {{Engineering A Verifier}}} \\[0.15in]
        {\fontsize{24}{24} \selectfont {{for Deep Neural Networks}}} \\[1in]    
        %{\fontsize{18}{18} \selectfont {{A Handbook for International Students}}} \\[1.in]

### 2024-10-15 faculty.tex
update

This section focuses on research publication, which is a major component of P\&T and of course in getting your name out there. P\&T evaluation requires no specific conferences/journals or numbers of papers, but typically you will want to have a good number of papers in top venues.
Work that won awards, e.g., best paper awards, can help a lot in P\&T. Papers with very high citations also help.  Research areas that you started and are now popular also count.  Finally, new research directions that can help get grants are also good.

@@

Successfully mentoring students is a key and most rewarding part of your job as a faculty member. 
There will be times when you feel discouraged and frustrated, but there will also be times when you feel proud and happy.

For P\&T you will need to successfully mentoring students.  Many universities expect you to need to graduate at least one PhD student to get tenure.

@@

\section{Mentoring Graduate Students}

>>>>

Research, in particular publications, is a major component of P\&T and of course in getting your name out there. P\&T evaluation requires no specific conferences/journals or numbers of papers, but typically you will want to have a good number of papers in top venues.
Papers and work that won awards, e.g., best paper awards, can help a lot in P\&T. Papers with very high citations also help.  Research areas that you started and are now popular also count.  Finally, new research directions that can help get grants are also good.

@@

Successfully mentoring students is import for P\&T process.  Many universities expect you to graduate at least one PhD student to get tenure.  
There will be times when you feel discouraged and frustrated, but there will also be times when you feel proud and happy.  In short, mentoring students is a key and most rewarding part of your job as a faculty member.

@@

\section{Mentoring Graduate Students}
You will need to mentor PhD students and help them find research topics, do research, publish papers, and become independent researchers. This is a long and challenging process, but it is also very rewarding.
